sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-26 doc/paper.Rmd
Tweak table

```{r compare-table}
library(kableExtra)
suppressMessages(suppressWarnings(d <- readr::read_csv(here::here("doc/software-comparison.csv"), show_col_types = FALSE, comment = "#")))
d <- as.matrix(d)
d[d == "1"] <- "\\checkmark"
d[d == "1*"] <- "\\checkmark\\footnote{a}"
d[d == "0"] <- "--"
d[d == "0*"] <- "--\\footnote{a}"
d <- as.data.frame(d)
names(d)[1] <- ""
row.names(d) <- NULL
d <- d[,c(1, 2, 3, 5, 6, 4, 7, 8, 9)]
names(d)[names(d) == "mgcv"] <- "mgcv\\footnote{a}"

knitr::kable(d, format = "latex", caption = "Comparison of functionality between eight R packages that can fit geostatistical GLMMs.", 
  booktabs = TRUE, 
  linesep = c(
    rep('', 5), # coefs
    '\\addlinespace',
    rep('', 5), # correlation stuff
    '\\addlinespace',
    rep('', 11), # likelihood
    '\\addlinespace',
    rep('', 2), # bayes
    '\\addlinespace'
  ),
  escape = FALSE, row.names = FALSE) %>%
  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::footnote(
    number = c(
      "SPDE approach as in Miller et al. (2019).",
      "Technically possible but non-trivial.",
      "Zero-inflated NB2 only.",
      "Tweedie power parameter fixed for \\\\texttt{mgcv::gamm()}.",
      "Technically possible but non-trivial.",
      "Technically possible but non-trivial."
    ),
    escape = FALSE
  )
```

>>>>

```{r compare-table}
library(kableExtra)
suppressMessages(suppressWarnings(d <- readr::read_csv(here::here("doc/software-comparison.csv"), show_col_types = FALSE, comment = "#")))
d <- as.matrix(d)
d[d == "1"] <- "\\checkmark"
d[d == "1*"] <- "\\checkmark\\footnote{a}"
d[d == "GAMs*"] <- "GAMs\\footnote{a}"
d[d == "0"] <- "--"
d[d == "0*"] <- "--\\footnote{a}"
d <- as.data.frame(d)
names(d)[1] <- ""
row.names(d) <- NULL
d <- d[,c(1, 2, 3, 5, 6, 4, 7, 8, 9)]
# names(d)[names(d) == "mgcv"] <- "mgcv\\footnote{a}"
d$Hmsc <- NULL

knitr::kable(d, format = "latex", caption = "Comparison of functionality between eight R packages that can fit geostatistical GLMMs.", 
  booktabs = TRUE, 
  linesep = c(
    rep('', 4), # coefs
    '\\addlinespace',
    rep('', 5), # correlation stuff
    '\\addlinespace',
    rep('', 12), # likelihood
    '\\addlinespace',
    rep('', 2), # bayes
    '\\addlinespace'
  ),
  escape = FALSE, row.names = FALSE) %>%
  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::footnote(
    number = c(
      "Penalized smoother GAMs",
      "SPDE approach as in Miller et al. (2019)",
      "Technically possible but non-trivial",
      "Zero-inflated NB2 only",
      "Tweedie power parameter fixed for \\\\texttt{mgcv::gamm()}",
      "Technically possible but non-trivial",
      "Technically possible but non-trivial"
    ),
    escape = FALSE
  )
```
